Synthesis of production rules for glycans

### 2020-10-16 papers/sugar-synth/experiments.tex
benchmark

{\em Benchmark: }
We have applied our tool on four sets of molecules form
respiratory mucins of a cystic fibrosis patient (D1),
human chorionic gonadotropin from a cancer cell line (D2), horse chorionic gonadotropin (D3), and
hydra (D4)~\cite{Jaiman2018,hydra}.
The availability of clean data, where we are clear about the source and the collection
methodology used, limits our choices for the data.

@@

For D1, we synthesize the rules in 1.2 seconds. If we reduced any of the first
two parameters, we failed.
Giving an extra compartment in the first row did not impact the performance.
We synthesize the rules for D2, which is also our motivating example, in 0.4 seconds.
The performance of the tool is also robust against variations of the parameters.
We synthesize the rules for D3 in 0.9 seconds if we use optimal values for the parameter.
However, if we use too many resources or too little, the tool runs for a long time,
which is typical. The search in combinatorial space is highly sensitive to the parameters.

The synthesis for D4 takes a long time. We also observe the trade-off between the number of compartments
and the depth of the rules at the first and second row of D4.
For D3, we also learned large rules, i.e., they are adding many nodes at a single time.
Currently, the tool does not have any objective function to optimize the synthesized rules.
We are hoping to see more data sets such that we can develop a clearer picture
for a reasonable objective function.

>>>>

{\em Benchmark: }
We have applied our tool on three sets of real data (D1,D2,D3) and two sets of synthetic data (D4,D5). The molecules have been obtained from
respiratory mucins of a cystic fibrosis patient (D1),
horse chorionic gonadotropin (D2), SARS-CoV-2 spike protein T323/S325 (D3)~\cite{}.
The availability of clean data, where we are clear about the source and the collection
methodology used, limits our choices for the data.

@@

For D1, we synthesize the rules in 1.60 seconds. Even by reducing the first two parameters, we were able to synthesize the rules but it took longer time.
Giving an extra compartment in the third row did not impact the performance.  We also observe the trade-off between the number of compartments
and the depth of the rules at the second and third row of D1 and how it impacts performance.
We synthesize the rules for D2, involving runaway reactions,  in 7.97 seconds.
For D2, we also learned large rules, i.e., they are adding many nodes at a single time.
We synthesize the rules for D3 in 0.57 seconds. 
However, if we use too many resources or too little, the tool runs for a long time,
which is typical. The search in combinatorial space is highly sensitive to the parameters.

The synthesis for D4 takes 0.72 seconds. We can observe that by reducing the number of rules to learn, the tool fails to learn rules as it required minimum 7 rules.

Currently, the tool does not have any objective function to optimize the synthesized rules.
We are hoping to see more data sets such that we can develop a clearer picture
for a reasonable objective function.
